---
title: "MarkdownReport"
author: "Duccio Rocchini"
date: "2024-01-09"
output: html_document
---

# My first markdown document!

Here you can add some text if you want!

In this case you attain a result: 
```{r, eval=T}
2 + 3
```

In this case you do not:
```{r, eval=F}
2 + 3
```

Using proper packages; the imageRy package has been nuilt at Alma Mater for learning remote sensing:
```{r, eval=T}
library(imageRy)
```

Let's import tha data by listing them in imageRy:
```{r, eval=T}
im.list()
```

Importing the Mato grosso area image:
```{r, eval=T}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Importing the Mato grosso area image without warnings:
```{r, eval=T, warning=F}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Making a new plot of the Mato Grosso area with the NIR ontop of the green component of the RGB space:
```{r, eval=T}
im.plotRGB(mato1992, r=2, g=1, b=3)
```

Plotting several images altogether:
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=1)
```

Calculating spectral indices:
```{r, eval=T}
library(terra)
library(viridis)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
```

Calculating variability:
```{r, eval=T}
sd5 <- focal(mato1992[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=viridisc)
```

